Responsible Machine Learning\\\large{with Interpretable Models, Post-hoc Explanation, and Disparate Impact Testing}

### 2019-11-06 article-information-2019.tex
minor change

\vspace{-10pt}
\textsection \ref{ssec:not} \textbf{Notation}: for spaces, datasets, and models.\\
\indent \textsection \ref{ssec:data} \textbf{Training data}: simulated data with known feature importance and social bias characteristics and collected home mortgage data.\\
\indent \textsection \ref{ssec:models} \textbf{ML models}: interpretable XNN and constrained MGBM models.\\
\indent \textsection \ref{ssec:expl} \textbf{Post-hoc explanation techniques}: PD, ICE, and Shapley values.\\
\indent \textsection \ref{ssec:di}  \textbf{DI testing methods}: .\\
\indent \textsection \ref{ssec:soft} \textbf{Software resources}: GitHub repository for the results presented herein and utilized and useful Python packages.

>>>>

\vspace{-10pt}
\textsection \ref{ssec:not} \textbf{Notation}: for spaces, datasets, and models.\\
\indent \textsection \ref{ssec:data} \textbf{Training data}: simulated data with known feature importance and social bias characteristics and collected home mortgage data.\\
\indent \textsection \ref{ssec:models} \textbf{ML models}: interpretable XNN and constrained MGBM models.\\
\indent \textsection \ref{ssec:expl} \textbf{Post-hoc explanation techniques}: PD, ICE, and Shapley values.\\
\indent \textsection \ref{ssec:di}  \textbf{DI testing methods}: .\\
\indent \textsection \ref{ssec:soft} \textbf{Software resources}: GitHub repository for the presented results; utilized and potentially useful Python packages.
